timesliced_random_cell_selection

### 2018-11-15 src/timesliced_random_cell_selection.Rmd
package updates

```{r pre-install & load packages, include=FALSE}
packages <- c("raster", "dplyr", "data.table", "sp", "adehabitatHR")
source("../src/ipak.R")
ipak(packages)
```

>>>>

New package attempt to do this.... #include=FALSE

```{r pre-install & load packages, }
install.packages("pacman")
library(pacman)
p_load(raster, dplyr, data.table, sp, adehabitatHR, maptools)

#

#packages <- c("raster", "dplyr", "data.table", "sp", "adehabitatHR", "maptools")
#source("../src/ipak.R")
#ipak(packages)
```
